Visualization and analysis of probability distributions of large temporal data

### 2021-11-11 Rmd/05-conclusion.Rmd
structural changes proposed in the meeting today

# Conclusion and future plans {#ch:conclusion}

@@

## Future work

### Putting all functionalities on CRAN

I want to combine `hakear` and `gravitas` into a single R package for systematically exploring distributions of a smaller number of time series, whilst `gracsr` would offer the clustering framework for systematically exploring a large number of time series. I intend to run it via https://ropensci.org/software-review/ to further refine them for more exposure and efficiency.

@@

### Comparing our clustering method with other benchmark methods

Testing needs to be carried out with non-hierarchy based clustering methods to see whether the proposed distances perform better with other algorithms. It would also be helpful to know how much more value we obtain from considering distributions rather than aggregating time series data. In the case of smart meters, this could be accomplished by comparing the results while validating them against external data such as weather conditions, socioeconomic or other demographic factors of those households.

@@

### Check generalizability of our methods

>>>>

# Conclusion {#ch:conclusion}

This chapter summarizes the thesis content, covering original contributions, software development, and future ideas.

## Original contributions

@@

## Future ideas

<!-- ### Putting all functionalities on CRAN -->

<!-- I want to combine `hakear` and `gravitas` into a single R package for systematically exploring distributions of a smaller number of time series, whilst `gracsr` would offer the clustering framework for systematically exploring a large number of time series. I intend to run it via https://ropensci.org/software-review/ to further refine them for more exposure and efficiency. -->

@@

<!-- ### Comparing our clustering method with other benchmark methods -->

<!-- Testing needs to be carried out with non-hierarchy based clustering methods to see whether the proposed distances perform better with other algorithms. It would also be helpful to know how much more value we obtain from considering distributions rather than aggregating time series data. In the case of smart meters, this could be accomplished by comparing the results while validating them against external data such as weather conditions, socioeconomic or other demographic factors of those households. -->

@@

### Extend methods to other fields
